Data Formatting

### 2021-02-22 scripts/data_format.Rmd
change joining function
update for making phylogeny with vl data

viral loads
```{r}
vl <- data %>% dplyr::select(vl.4:vl.42) %>% distinct() %>% pivot_longer(vl.4:vl.42)
vl$species_code <- as.double(gsub("vl.","",vl$name))
vl %<>% full_join(., names, by="species_code")
vl %<>% mutate(., ln_value = log(value)) %>% mutate(., log10_value = log10(value))
```

@@

data for bar plots - primarily used by fig4
```{r}
#barplots comparing community composition
abundances <- comm_summ %>% inner_join(.,evenness)

>>>>

viral loads
```{r}
vl <- data %>% dplyr::select(vl.4:vl.42) %>% distinct() %>% pivot_longer(vl.4:vl.42)
vl %<>% mutate(species_code = as.double(gsub("vl.","",vl$name)))
vl %<>% full_join(., names, by="species_code")
vl %<>% mutate(name = gsub("_"," ",vl$species_name))
vl$value %<>% na_if(.,0)
vl %<>% mutate(., ln_value = log(value)) %>% mutate(., log10_value = log10(value))
vl %<>% replace_na(.,list(value=0,ln_value=0,log10_value=0))
```

@@

data for bar plots - primarily used by fig4
```{r}
#barplots comparing community composition
abundances <- comm_summ %>% full_join(.,evenness)
